% !TEX TS-program = LuaLaTeX

\documentclass[12pt]{article}

\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{scrextend}
\usepackage{etaremune}
\usepackage{mathptmx}
%\usepackage{tgtermes}
\usepackage{color}
\usepackage{etaremune}

% use http link for email
\usepackage[colorlinks = true,
          allcolors = PineGreen]{hyperref}            
            %
            
%allow formula formatting
\usepackage{amsmath}
%\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
\usepackage{comment}

%title positon
\usepackage{titling} %fix title
\setlength{\droptitle}{-6em}   % Move up the title 

%change section title font size
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\fontsize{12}{15}}{\thesection}{1em}{}[{\titlerule[0.5pt]}]
  
\titleformat{\subsection}
  {\normalfont\fontsize{12}{13}}{\thesection}{1em}{}

% change page margin and cancel identation
\usepackage[top=0.6in, bottom=0.8in, left=0.5in, right=0.5in]{geometry} 
\setlength{\parindent}{0pt}


%allow modifying section titles 
\usepackage[dvipsnames]{xcolor}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0in}
  }
}{
  \end{list}
}

\begin{document}
\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%
\begin{center}
	\textbf{
			{\huge I}{\Large SABEL} \hspace{-0.1em} 
			{\huge R}{\Large OSE} \hspace{-0.1em} 
			{\huge F}{\Large ULCHER}}\\
\end{center}
\begin{minipage}[t]{0.5\linewidth}
\begin{flushleft}
	\MYhref[black]{mailto:isabelfulcher@g.harvard.edu}{isabelfulcher@g.harvard.edu} \\
	\MYhref[black]{http://orcid.org/0000-0002-1209-824X}{ORCID: 0000-0002-1209-824X} 
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth} 
\begin{flushright}  
	%\vspace*{1mm} 
	{\LARGE
		\href[pdfnewwindow=true]{http://isabelfulcher.github.io}{\faGlobe} \href{https://github.com/isabelfulcher}{\faGithub}  \href{https://scholar.google.com/citations?user=0-9RLbQAAAAJ&hl=en}{\faGoogle}  \href{mailto:isabelfulcher@g.harvard.edu}{\faEnvelope }   \par
	}
\end{flushright}  
\end{minipage}

\section*{\textbf{{\large E}DUCATION}}

\textbf{Harvard University} \hfill \hfill \textbf{Cambridge, MA}

Doctor of Philosophy, Biostatistics \hfill \hfill March 2019 \\
%Dissertation Advisor: Eric Tchetgen Tchetgen, PhD \\

\textbf{Harvard University} \hfill \hfill \textbf{Cambridge, MA}

Masters of Arts, Biostatistics \hfill \hfill May 2016

\vspace{.5cm}

\textbf{McGill University} \hfill \hfill \textbf{Montreal, QC} \\
Bachelor of Arts and Science, Mathematics and Anthropology  \hfill \hfill May 2012 


%% Research Experience
\section*{\textbf{{\large R}ESEARCH {\large E}XPERIENCE }}

\textbf{Department of Global Health and Social Medicine, Harvard Medical School \hfill \hfill Boston, MA} \\
\textit{Postdoctoral Fellow} \hfill \hfill January 2019 -- Present \\
Supervised by: Bethany Hedt-Gauthier, PhD and Eric Tchetgen Tchetgen, PhD 
\begin{addmargin}[1em]{2em} {\small Development and application of causal inference methods to evaluate a mHealth-based community health worker intervention in Zanzibar, Tanzania on facility delivery, maternal outcomes, and early childhood development.} \end{addmargin} 
\vspace{.2cm}
\textbf{Department of Biostatistics, Harvard T.H. Chan School of Public Health \hfill \hfill Boston, MA} \\
\textit{Doctoral Candidate}  \hfill \hfill January 2016 -- November 2018 \\
Dissertation Advisor: Eric Tchetgen Tchetgen, PhD \\
Dissertation Title: ``Statistical Inference for Causal Mechanisms: Mediation and Interference" 


%% Consulting Experience
\section*{\textbf{{\large C}{ONSULTING} \& {\large I}{NDUSTRY} {\large E}{XPERIENCE}}}
\textbf{Research Center, Planned Parenthood League of Massachusetts \hfill \hfill Boston, MA}  \\
\textit{Statistician} \hfill \hfill August 2017 -- Present 
\begin{addmargin}[1em]{2em} {\small Leading statistical analyses on two major studies that aim to evaluate: (1) the impact of the Massachusetts's parental consent law on contraceptive choice among minors; (2) quality of care received by opioid users; (3) inequities in contraceptive autonomy by ability status, gender identity, race, and educational level} \\ \end{addmargin} 

\textbf{Safer Deliveries Program, D-tree International \hfill \hfill Zanzibar, Tanzania} \\
\textit{Researcher} \hfill \hfill May 2017 -- Present 
\begin{addmargin}[1em]{2em} {\small Conduct research and evaluation question development, analysis planning, and application of statistical methods to assess the program's effectiveness at reducing high rates of maternal and neonatal mortality in Zanzibar} \\ \end{addmargin} 

%\textbf{Department of OB/GYN/RS, University of Pittsburgh School of Medicine \hfill \hfill Pittsburgh, PA}  \\
%\textit{ Statistical Consultant} \hfill \hfill April 2018 \\
%\begin{addmargin}[1em]{2em} {\small Assessed long-term impact of laparoscopic excision of endometriosis on pain reduction and quality of life improvement} \\ \end{addmargin} 

\textbf{ZS Associates \hfill \hfill Evanston, IL} \\
\textit{Business Associate} \hfill \hfill September 2012 -- July 2014 
\begin{addmargin}[1em]{2em} {\small Engaged with global pharmaceutical and biotech companies on a variety of market research projects for drugs and their indications. Created and fielded surveys, conducted in-person interviews, and led statistical analyses.} \end{addmargin}

%% Teaching Experience
\section*{\textbf{{\large T}{EACHING} {\large E}{XPERIENCE}}}
\textbf{Harvard T.H. Chan School of Public Health \hfill \hfill Boston, MA} \\
\textit{Instructor}, Biostatistics Preparatory Course: Methods and Computing in R \hfill \hfill Summer 2018 \\
\textit{Instructor}, Stata Orientation for Incoming Graduate Students \hfill \hfill	Summer 2016, 2017, 2018\\
\textit{Graduate Student Mentor}, Pipelines into Biostatistics Summer Program \hfill \hfill Summer 2018 \\
\textit{Teaching Fellow}, Global Initiative for Neuropsychiatric Genetics Education in Research \hfill \hfill Spring 2018 \\
\textit{Head Teaching Assistant}, ID 201: Core Principles of Biostatistics and Epidemiology \hfill \hfill Fall 2015, 2016, 2017 \\
\textit{Teaching Assistant}, HPM 543: Quantitative Methods in Program Evaluation \hfill \hfill Spring 2017 \\
\textit{Teaching Assistant}, BIO 507: Methods for Monitoring and Evaluation \hfill \hfill Spring 2016 \\

\textbf{University of Global Health Equity \hfill \hfill Kigali, Rwanda} \\
\textit{Teaching Assistant}, Program Monitoring, Evaluation, and Research Methods  \hfill \hfill Spring 2017, 2018 \\

\textbf{D-tree International \hfill \hfill Zanzibar, Tanzania}\\
\textit{Instructor}, Data Analysis and Stata Software Training Course \hfill \hfill Summer 2017  \\

\textbf{McGill University \hfill \hfill Montreal, QC}\\
\textit{Teaching Assistant}, MATH 323: Probability \hfill \hfill Fall 2010, 2011 \\
\textit{Teaching Assistant}, MATH 324: Statistics \hfill \hfill Spring 2012 

\vspace{-.1cm}
%% Honors and Awards
\section*{\textbf{{\large H}{ONORS} {\large \&} {\large A}{WARDS}}}
\textbf{University of Florida Statistics Workshop Travel Award} \hfill \hfill 2019 \\
\textbf{National Science Foundation Travel Award} {\footnotesize (1 of 5 best posters at Atlantic Causal Inference Conference)}\hfill \hfill	2018 \\
\textbf{Barry R. and Irene Tilenius Bloom Fellowship} {\footnotesize (full funding for the 2017-2018 academic year)}\hfill \hfill	2018 \\
\textbf{Harvard University Distinction in Teaching} {\footnotesize (outstanding teaching assistant award for the 2016-2017 academic year)}\hfill \hfill 2017 \\
\textbf{Rose Traveling Fellowship} {\footnotesize (funding for international research)} \hfill \hfill	2017 \\
\textbf{Maternal Health Task Force Travel Award} {\footnotesize (funding for international maternal health research)} \hfill \hfill	2017 \\
\textbf{Statistics in Epidemiology Young Investigator Award} {\footnotesize (1 of 3 best papers in Epidemiology)}  \hfill \hfill	2017 \\
\textbf{McGill University Dean's Honour List} {\footnotesize (awarded to top 10\% of graduating class; highest graduating honor)}  \hfill \hfill	2012 \\
\textbf{McGill University Golden Key Society} {\footnotesize (awarded to top 15\% of class)}  \hfill \hfill2010, 2011, 2012 

% Peer-Reviewed Publications
\section*{\textbf{{\large P}{UBLICATIONS}}}

\subsection*{\textbf{PEER REVIEWED}}

\begin{etaremune}
\item \textbf{Fulcher, I. R.}, Shi, X., \& Tchetgen Tchetgen, E. J. (2019). Estimation of natural indirect effects robust to unmeasured confounding and mediator measurement error. \textit{In press} at Epidemiology. arXiv preprint arXiv:1808.03692.  

\item Janiak, E., \textbf{Fulcher, I. R.}, ..., \& Goldberg, A. (2019). Impact of Massachusetts' parental involvement law on procedural timing among adolescents seeking abortion. \textit{In press} at Obstetrics \& Gynecology.

\item Bao, E.L., Lareau, C. A., Brugnara, C., \textbf{Fulcher, I. R.} et al. (2019). Heritability of fetal hemoglobin, white cell count, and other clinical traits from a sickle cell disease family cohort. American Journal of Hematology. DOI: 10.1002/ajh.25421. 

\item \textbf{Fulcher, I. R.}, Tchetgen Tchetgen E. J., \& Williams, P. L. (2017). Mediation analysis for censored survival data under an accelerated failure time model.  Epidemiology, 28(5), 660-666. 

\end{etaremune}

\subsection*{\textbf{PRE-PRINTS}}

\begin{enumerate}
	\item Tchetgen Tchetgen, E. J., \textbf{Fulcher, I. R.}, and Shpitser, I. (2018). Auto-g-computation of causal effects on a network. \textit{In revision} at Journal of American Statistical Association. arXiv preprint arXiv:1709.01577. 
	
	\item \textbf{Fulcher, I. R.}, Shpitser, I., \& Tchetgen Tchetgen, E. J. (2018). Robust inference on indirect causal effects.  \textit{In revision} at Journal of the Royal Statistical Society Series B. arXiv preprint arXiv:1711.03611. 
\end{enumerate}

%\textbf{Fulcher, I. R.}, Lareau, C., Shpitser, I., \& Tchetgen Tchetgen, E. J. (2018). Bayesian auto-g-computation of network causal effects: incarceration and infection in a high risk network. \textit{In revision} at Journal of Royal Statistical Society Series A. \\

%\textbf{Fulcher, I. R.}, Hedt, K., Marealle, S., Abdalla O., Tibaijuka, J., Hoffman, R., Layer, E., and Hedt-Gauthier, B. (2019). Errors in estimated gestational ages reduce the likelihood of health facility deliveries: results from an observational cohort study in Zanzibar. \textit{Submitted} to BMC Health Services Research.

%Endo

%Minors


% Presentations
\section*{\textbf{{\large P}{RESENTATIONS}}}

%\subsection*{\textbf{INVITED}}


%\subsection*{\textbf{CONFERENCE CONTRIBUTED}}

``Estimation of natural indirect effects robust to unmeasured confounding and mediator measurement error.'' Poster session at: University of Florida Winter Workshop, Gainesville, FL (2019). \\

``Auto-g-computation of causal effects on a sexual and injection-drug use network.'' Poster session at: Harvard Data Science Conference, Cambridge, MA (2018). \\

``Auto-g-computation of causal effects on a sexual and injection-drug use network.'' Center for Causal Inference Working Group, University of Pennsylvania, Philadelphia, PA (2018). \\

``Working Towards Safer Deliveries in Zanzibar, Tanzania.''  Poster session at: Future Health Campaign Celebration, Harvard T.H. Chan School of Public Health, Boston, MA (2018). \\

``Auto-g-computation of causal effects on a sexual and injection-drug use network.'' Department of Biostatistics HIV Working Group, Harvard University, Cambridge, MA (2018). \\

``Nonparametric identification and robust estimation of indirect causal effects in the presence of exposure-outcome confounding.'' Poster session at: Atlantic Causal Inference Conference, Pittsburgh, PA (2018). \\

``The Generalized Front-Door Formula for Estimation of Indirect Causal Effects of a Confounded Treatment.'' ENAR Spring Meeting, Atlanta, GA (2018). \\

``Data for decision-making in digital health programs: how analysis of routine data from the Safer Deliveries program in Zanzibar improved program implementation and mothers' outcomes.'' Global Digital Health Forum, Washington, DC (2017). \\

``Mediation Analysis for Censored Survival Data under an Accelerated Failure Time Model.'' Joint Statistical Meetings, Baltimore, MD (2017). \\

``The Generalized Front-door Formula for Identification of Partial Causal Effects.'' ENAR Spring Meeting, Washington, DC (2017). \\

``Mediation Analysis for Censored Survival Data under an Accelerated Failure Time Model.'' ENAR Spring Meeting, Austin, TX (2016). 


% Software
\section*{\textbf{{\large S}{OFTWARE}}}

{\bf \href{https://isabelfulcher.github.io/frontdoorpiie/}{frontdoorpiie}} (R package) Estimation and inference for the Population Intervention Indirect Effect \\
\vspace{-.3cm}

{\bf \href{https://isabelfulcher.github.io/autognet/}{autognet}} (R package) Auto-g-computation for estimation of network causal effects

\end{document}